Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-06-12 04_paper/Draft2.Rmd
more changes to draft 2

However, many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "South-South cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We tackle this question by considering Chinese media coverage of developing countries intended for foreign audiences and China's bilateral diplomatic activities. These measures capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China's development finance complements these goals, we expect greater coverage of a developing country in a Chinese official media outlet directed to foreign readers and greater bilateral diplomatic activity to correlate with greater Chinese foreign aid giving.

To test this expectation, we merge AidData's Chinese development finance dataset with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy-seeking objectives on the world stage.

@@

As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret. But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.[^4] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing. Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA). However, while established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^5]

@@

Nonetheless, absent transparency in reporting, it has proved difficult to provide direct confirmation that China's foreign aid is motivated by such public goals as south-south diplomacy and international legitimacy. However, newly available datasets offer an opportunity to empirically probe these motives. In this study, we explore the connections between China's bilateral development finance and critical *visible* activities linked to the diplomatic and legitimacy-seeking objectives scholars attribute to China's international development finance. We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing state-run media.

@@

First, they signal the importance of developing countries to Beijing. Just like development finance, diplomatic trips and media coverage are subject to scarcity---the first in terms of limited resources and bandwidth; the second in terms of time dedicated to writing, editing, and publishing content. Within the rationalist framework most often adopted by IR scholars who study international aid, this implies a direct correspondence between the countries that host diplomatic visits and that are subjects of state-sponsored news articles and the importance of developing countries to China. In short, visits and coverage are costly, and they therefore tell us something about which developing countries Beijing values most.

@@

# Media

## First-level Agenda-setting

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country, in particular, to the public. That is, the public learns the importance of objects based on the amount of coverage that those objects receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues (@mccombs_agenda-setting_1972). More specifically, as @berelson_mass_1966 observe, "The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public. The vast majority support this agenda-setting notion (need some more extension or citations here).

Over decades of rich research in agenda-setting, empirical patterns support @cohen_press_1963's famous notation that the media is "stunningly successful in telling its readers what to think *about*" (p. 13; emphasis added). That is, the salience of news media reports transfers to the perception of issue salience to the public (@mccombs_agenda-setting_1972). Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals' perceptions of the relative importance and salience of the issues.

To extend this logic, media salience indicates significance for foreign countries named in the media. @wanta_agenda_2004-3 show coverage of foreign nations in the news relates to the perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the U.S. The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.

## Selective Media Attention

With the implication of the media salience in mind, editor is a source of gatekeeping power for those who can tell us where to focus our attention. From the perspectives of news outlets, limited by time and space, editors can only select a handful of stories while leaving dozens of new stories off the air. News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.

Also, previous findings show the strategic consideration of news editors in considering what international news gets media cover. Not all countries in the world receive equal coverage. In fact, only a small portion of international events can get through the media gatekeepers and get media coverage. While most powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered. @golan_international_2003-1's study examines how 138 elections held between 1998 and 2000 were covered by the U.S. network television newscasts (ABC, CBS, NBC and CNN). They found that elections in Europe, Asia or the Middle East received substantial coverage than those in Latin America and Africa. A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, geopolitical position in the world system as key predictors of coverage (@sheafer_relative_2014-1). Hence, if foreign countries receive more media coverage, the increased media salience suggests the salience of the foreign countries to the audiences and the newsworthiness to the news editors.

## Second-level Agenda-setting

In addition to swaying people's attention, media agenda-setting is also critical in building states' image to international audiences. @nye_public_2008-2 suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications, with an aim to improve the country's "soft power". Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press. China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by an emerging international press.

Recent research in the explication of the second-level agenda-setting connects the concept of framing and suggests that news media attention can influence how people think about a topic by emphasizing certain attributes than others (@entman_theorizing_2008; @kiousis_international_2008). Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes. Improving one's image to foreign audiences is the core objective of mediated public diplomacy.

As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency. It has had a dual role: reporting news and building the China image as part of Beijing's "going out" strategy (@shambaugh_chinas_2015-1). It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires. The agency targets developing countries, where the Western press has contracted in recent years due to the decline of advertisement revenues and had a smaller presence oversea. It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more view-friendly format. Governments use media to tell its story to the world and improve its public relations with other countries. As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*. That is, to study how government-sponsored international broadcasting contributes to influencing the public or elite opinion among foreign countries (@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009).

Despite growing in the global media landscape, *Xinhua*, as an international broadcaster, needs foreign audiences. Simply providing more information will not improve their image in the Western world. Attracting audiences depends on credibility, a state-sponsored-image-construction news outlet would typically lack. As @druckman_limits_2001 presents, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations. On the other hand, *Xinhua* needs to maintain a low political bias and higher professional standard to assert its brand and increase its international competitiveness.

Hence, while *Xinhua* plays a major role in defining, shaping and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors. Taking into account the limited space of *Xinhua* to report global affairs, editors' choices reflect which countries are more than the others to receive media coverage.

@@

Previous sections illustrate media agenda setting as an essential step in a country's public diplomacy process to influence the public's opinion in a second country. For example, building international media outreach to have a space in the global marketplace of ideas are the Chinese government's crucial step to "speak to [foreign] people -- and listen to them" (@hoffman_introduction_1968, p. 4). In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audience" (@deibel_culture_1976, p. 15).

An image that fits into a traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" (@deibel_culture_1976, p. 13). In addition to negotiations behind closed doors, records of visits have symbolic evidence to show the bilateral relationships between countries. The elite-level diplomacy, government-to-government diplomatic visit, is the focus in this section. Government-to-government visits are important as leaders' resources are scarce. They often mark the further development in bilateral relations, especially in furthering the visiting and host countries' bilateral trade relationships (@nitsch_state_2005). Leader visits also have implications on the host leaders' security in office (@malis_state_2021) and the states' security issues (@mcmanus_making_2018). In all, diplomatic visits send important an important positive signal that the visiting and hosting countries support each other and have closer relationships.

Visiting leaders can increase the awareness of themselves and their country among citizens in the host country. @goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual. U.S. visits had large and positive impact until the international media reported the negative aspects of the "war on terror" in Iraq. Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy. The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect. The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries (@goldsmith_does_2021). In most cases, the host leader has leverage to provide frame for the journalists to report the government-to-government visit that is expected to receive positive coverage.

In short, diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations. From the perspective of communication, diplomatic visit is a signal of support and proximity of the countries. The public outreach of diplomatic visits also has profound implications in public diplomacy: elites in the visiting country usually improve the image of their country through visits.

@@

However, while public diplomacy is one way to increase a state's soft power, in the end, visits and media are fleeting and symbolic. To reinforce the objectives pursued through these visible acts of diplomacy, we argue that Beijing uses other tools, such as foreign aid, to provide tangible and material support to important countries. Hence, we expect that to the extent that Beijing uses foreign aid as a tool in support of these particular foreign policy goals, we should see Chinese development finance parallel these different but complementary activities. This rationale leads to our hypotheses:

@@

To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData's Chinese development finance dataset [@dreherEtAl2021 and @dreherEtAl2022] with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China [@aidData2021] and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research [-@cline2022]. The full dataset consists of unique recipient-year observations from 2000 to 2014.[^6]

[^6]: Version 1.0 of the Chinese development finance dataset may be obtained at: <http://aiddata.org/data/chinese-global-official-finance-dataset>. The data on China's public diplomacy can be obtained at: <http://china-dashboard.aiddata.org/>. Finally, the Archer portal used to access extracted features in the Global News Index at the Cline Center can be found at: <https://databank.illinois.edu/datasets/IDB-2179938>.

@@

The first set of controls consist of aid recipient characteristics. From the Penn World Table (version 9.1), we use real gross domestic product (GDP) in millions of 2011 USD. This serves as a proxy for the size of a recipient's economy. From the Penn World Table we also use population in millions and the number of people employed in millions. We normalize values using ihs to keep the transformation of the data consistent with that of the response. From the Institute for Health Metrics and Evaluation we use a yearly count of the number of individuals killed by natural disasters, and we again apply the ihs transformation. From PRIO/UCDP we use a binary measure of the presence of civil war, coded as 1 for each year where there is armed violence between two or more parties where one of the parties is the government and at least 25 battle-related deaths occur. To capture political and civil liberties we use Freedom House and adjust values so that higher values denote greater levels of freedom. We use this measure instead of Polity to avoid collinearities with civil war.

We further control for bilateral characteristics between China and aid recipients. To account for economic ties we use total bilateral trade (imports plus exports) in millions of dollars. From ATOP we use a binary measure of alliances between recipients and China. This measure is coded as 1 if there is at least one of either a formal offensive, defensive, non-aggression, or neutrality agreement. Finally, form CEPII we use a measure of bilateral distance in kilometers between recipients and China. Both trade and distance are transformed using ihs.

@@

Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014. Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.[^7] Summary statistics are shown the Appendix.

[^7]: For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.

@@

```{r, echo=FALSE}
coef_table <- map_dfr(
  model_list,
  ~ estimatr::tidy(lmtest::coeftest(.x))
) %>%
  filter(
    str_detect(term, "count") | 
      str_detect(term, "visits")
  ) %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    term = rep(c("Coverage", "Visits"), len = n())
  ) %>%
  select(term, estimate, conf.low, conf.high)
tibble(
  "1" = coef_table$term[1:2],
  "2" = coef_table$estimate[1:2],
  "3" = " ",
  "4" = coef_table$estimate[3:4],
  "5" = " ",
  "6" = coef_table$estimate[5:6],
  "7" = " ",
  "8" = coef_table$estimate[7:8],
  "9" = " ",
  "10" = coef_table$estimate[9:10],
  "11" = " ",
  "12" = coef_table$estimate[11:12],
  "13" = " "
) %>% 
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  kable(booktabs = T,
        format = "latex",
        caption = "Table 1: Model Estimates",
        col.names = c(
          " ", rep(c("Est.", "95% CI"), len = 12)
        )) %>%
  kable_classic(full_width = F) %>%
  column_spec(
    3, image = spec_pointrange(
      x = coef_table$estimate[1:2],
      xmin = coef_table$conf.low[1:2],
      xmax = coef_table$conf.high[1:2],
      vline = 0
    )
  ) %>%
  column_spec(
    5, image = spec_pointrange(
      x = coef_table$estimate[3:4],
      xmin = coef_table$conf.low[3:4],
      xmax = coef_table$conf.high[3:4],
      vline = 0
    )
  ) %>%
  column_spec(
    7, image = spec_pointrange(
      x = coef_table$estimate[5:6],
      xmin = coef_table$conf.low[5:6],
      xmax = coef_table$conf.high[5:6],
      vline = 0,
      lim = c(0, max(coef_table$conf.high[5:6]))
    )
  ) %>%
  column_spec(
    9, image = spec_pointrange(
      x = coef_table$estimate[7:8],
      xmin = coef_table$conf.low[7:8],
      xmax = coef_table$conf.high[7:8],
      vline = 0
    )
  )%>%
  column_spec(
    11, image = spec_pointrange(
      x = coef_table$estimate[9:10],
      xmin = coef_table$conf.low[9:10],
      xmax = coef_table$conf.high[9:10],
      vline = 0
    )
  ) %>%
  column_spec(
    13, image = spec_pointrange(
      x = coef_table$estimate[11:12],
      xmin = coef_table$conf.low[11:12],
      xmax = coef_table$conf.high[11:12],
      vline = 0
    )
  ) %>%
  add_header_above(
    c(
      " " = 1,
      "Linear" = 2,
      "Tobit" = 2,
      "Selection" = 2,
      "Level" = 2,
      "IV Lag" = 2,
      "IV Lewbel" = 2
    )
  ) %>% cat

>>>>

While limited transparency is the norm for Beijing, in the context of its global development finance the lack of transparency is a puzzle. Many observe an unmistakable connection between China's version of Official Development Assistance (ODA) and its political and material foreign policy goals. These ambitions include international recognition and closer diplomatic ties with recipients in what China calls "South-South cooperation." While distinct, these objectives have one thing in common: they are difficult to accomplish *in secret.* They require visibility. So, absent traditional modes of transparency, *how does China's foreign aid relate to Beijing's efforts at public diplomacy and international recognition?*

We probe this question empirically by exploiting two newly available datasets of Chinese media coverage of developing countries intended for foreign audiences and of China's bilateral diplomatic visits, respectively. These activities capture two distinct but related aspects of China's foreign policy: status/legitimacy in the eyes of a foreign (predominantly Western) audience and south-south diplomacy. To the extent that China's development finance is targeted at these goals, we expect China to complement greater state-run media coverage of developing countries and greater bilateral diplomatic activity with greater development finance.

To test this expectation, we merge AidData's Chinese development finance dataset with: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research. We find that greater media coverage of developing countries targeted at a foreign audience via the English version of *Xinhua* and the number of diplomatic visits to a developing country predict greater receipt of Chinese aid. Our results support the view that Chinese aid allocation patterns map to China's broader diplomacy and legitimacy-seeking objectives on the world stage.

@@

As @fuchsRudyak2019 point out, the obscurity of China's development finance creates the perception among Western donors that China purposefully keeps its aid giving a secret. But as several scholars note, lack of transparency may have more to do with capacity and logistics than intention.[^4] For many decades, a complex and fractured bureaucracy has orchestrated Beijing's development financing. Only in the past few years, as its goals have become ever loftier, did China establish its first true bilateral aid agency---the China International Development Cooperation Agency (CIDCA). While it was established in 2018, much work remains to consolidate the operation and management of China's bilateral aid.[^5]

@@

Absent transparency, how does Beijing leverage its global development finance in support of its diplomatic interests and international recognition? In this paper, we seek out an answer by looking at other kinds of visible foreign policy activities. We exploit two newly available datasets to explore the connections between China's bilateral development finance and critical *visible* activities linked to the diplomatic and legitimacy-seeking objectives scholars attribute to China's international development finance. We focus in particular on two factors: (1) diplomatic visits from China to developing countries and (2) coverage of developing countries in external-facing state-run media.

@@

First, they signal the importance of developing countries to Beijing. Just like development finance, diplomatic visits and state-run media coverage are subject to scarcity---the first in terms of limited resources and bandwidth; the second in terms of time dedicated to writing, editing, and publishing content. Within the rationalist framework most often adopted by IR scholars who study international aid,[^6] this implies a direct correspondence between the countries that host diplomatic visits and that are subjects of state-sponsored news articles and the importance of developing countries to China. In short, visits and coverage are costly, and they therefore tell us something about which developing countries Beijing values most.

[^6]: @bermeo2018 and @BDM2009 are exemplary examples of IR research in international aid that falls within the rationalist tradition.

@@

# Xinhua and Setting the Agenda

Media agenda-setting is critical in building a state's image to international audiences. @nye_public_2008-2 suggests that the first and the most immediate dimension of investing in public diplomacy is through daily communications with the aim to improve a country's "soft power". Government officials devote a great deal of attention to what and how to tell the press, both the domestic press and the foreign press. For this reason, China has expanded its *Xinhua* News Agency to reach global audiences during the past decade to take greater control of how it is portrayed by the international press.

As a state-sponsored media platform, *Xinhua* News Agency is often considered more than a news media agency. It has had a dual role: reporting news and building up China's image abroad as part of Beijing's "going out" strategy [@shambaugh_chinas_2015-1]. It has opened over 170 bureaus across the globe and competes head-to-head with the main Western newswires. Among many audiences, the agency targets developing countries, where the Western press has contracted out in recent years due to the decline of advertisement revenues. It is an international news agency that tries to alter its stilted and propagandistic flavor and package its content in a more viewer-friendly format. Beijing uses media to tell its story to the world and improve its public relations with other countries. As such, scholars often focus on Chinese mediated public diplomacy efforts through *Xinhua*. That is, they study how government-sponsored international broadcasting contributes to influencing public or elite opinion among foreign countries [@entman_theorizing_2008; @manheim_strategic_1994; @sheafer_mediated_2009)]

Despite growing in the global media landscape, *Xinhua*, as an international broadcaster, needs foreign audiences. Simply providing more information will not improve their image in the Western world. As @druckman_limits_2001 notes, one conditional factor in influencing public opinion (especially foreign audiences'), is an information sender's "credibility." On the one hand, governments attempt to positively shape the global narrative regarding their leaders and foreign policies using their own newsgathering and broadcasting operations. On the other hand, *Xinhua* needs to maintain low political bias and higher professional standards to assert its brand and increase its international competitiveness.

Hence, while *Xinhua* plays a major role in defining, shaping, and projecting China's image, its primary function is to transmit information. It reports on a variety of global issues with different regional focuses to meet the standard of international news competitors.

However, mere information transmission is rarely a neutral act. It reflects certain priorities, which in turn effect the priorities and perceptions of audiences. Research on the first-level and second-level agenda-setting power of media illustrates this fact.

## First and Second Level Agenda-Setting

Agenda-setting refers to the ability of media to signal to the public what is important. Media coverage of a foreign country measures how important a country is to its reporting country and, in particular, to the public. The public learns the importance of issues based on the amount of coverage that those issues receive. Agenda-setting theory suggests that mass media serve as one of the key sources for public perception of important issues [@mccombs_agenda-setting_1972]. More specifically, as @berelson_mass_1966 observe, "The mass media force attention to certain issues. They build up public images of political figures. They are constantly presenting objects suggesting what individuals in the mass should think about, know about, have feelings about" (p. 468). Since their seminal work, hundreds of studies have examined this media effect on the public. The vast majority support this agenda-setting notion (need some more extension or citations here).

Over decades of rich research in agenda-setting, empirical patterns support Cohen's [-@cohen_press_1963] idea that the media is "stunningly successful in telling its readers what to think *about*" (p. 13; emphasis added). That is, the salience of news media reports transfers to the perception of issue salience to the public [@mccombs_agenda-setting_1972]. Extensive media coverage provides news consumers with salience cues regarding the importance of the political figures or issues, and in turn shape individuals' perceptions of the relative importance and salience of the issues.

To extend this logic, media salience indicates the significance of foreign countries named in the media. @wanta_agenda_2004-3 show that coverage of foreign nations in the news in the US relates to respondents' perception of the importance of the countries: the more coverage a state receives, the more likely respondents think the state is vitally important to the US. The media coverage of the countries will lead to the countries as a whole becoming more salient among the public.

Recent research on what is called second-level agenda-setting suggests that news media can influence how people think about a topic by emphasizing certain issues or subjects over and above others [@entman_theorizing_2008; @kiousis_international_2008]. Compared to the first-level agenda-setting, this mechanism entails a deeper media influence on shaping public attitudes. Rather simply focusing on what the public thinks about more, second-level agenda setting emphasizes media's ability to shape how the public think about issues. In the case of *Xinhua*, this implies an ability to shape how foreign audiences perceive the countries covered by the news service.

## Editorial Gatekeeping and Scarcity

When it comes to agenda-setting, the *editor* is a critical source of gatekeeping power. From the perspective of news outlets, limited by time and space, editors can only select a handful of stories while relegating many others to file drawer. News selection is at the heart of the agenda-setting process since the issues that fail to pass through the gatekeepers of the news also fail to give salience cues regarding the relative importance of the issues.

Also, previous findings show the strategic consideration of news editors in considering what international news gets media coveriage. Not all countries in the world receive equal coverage. In fact, only a small portion of international events get through the media gatekeepers. While powerful core states consistently receive higher amounts of coverage from newscasts, small peripheral states remain largely uncovered. @golan_international_2003-1's study examines how 138 elections held between 1998 and 2000 were covered by US network television newscasts (ABC, CBS, NBC and CNN). They found that elections in Europe, Asia or the Middle East received more substantial coverage than those in Latin America and Africa. A large body of literature has examined the determinants of international news coverage and has identified variables such as geographic locations, cultural proximity, and geopolitical position in the world system as key predictors of coverage [@sheafer_relative_2014-1]

It seems unlikely that *Xinhua* would be an exception to the rule that biases exist in the gatekeeping decisions of editors. However, in the case of *Xinhua*, given the discussion of its role in China's "going out" strategy, it seems reasonable that its bias will be in favor of countries that are important to Beijing. In particular, it will cover countries that are important to Beijing's foreign policy goals.

@@

The previous section illustrates that media agenda-setting is an essential step in a country's public diplomacy as it tries to influence the perceptions of a foreign audience. To borrow from one media scholar, external facing media allow Beijing to "speak to [foreign] people -- and listen to them" [@hoffman_introduction_1968, 4] In fact, all public diplomacy programs have a primary responsibility to explain and defend government policies to foreign audiences" [@deibel_culture_1976, 15].

A traditional mental image of public diplomacy is "diplomats engaged in traditional negotiations under the glare of publicity" [@deibel_culture_1976, 13]. In addition to negotiations behind closed doors, records of visits provide symbolic evidence of the bilateral relationship between countries. Perhaps most importantly, government-to-government visits are not costless---they require time and resources to orchestrate and enact. They often are meant to develop and strengthen bilateral relations, especially with respect to bilateral trade [@nitsch_state_2005]. Leader visits also have implications on the host leaders' security in office [@malis_state_2021] and on the host state's security in general [@mcmanus_making_2018]. In all, diplomatic visits send an important signal that the visiting and hosting countries support each other and have a close relationship.

Visiting leaders also can increase awareness of themselves among citizens in the host country. @goldsmith_spinning_2009 find that the impact of high-level government visits on foreign publics' opinions is contextual. US visits had large and positive impacts until the international media reported the negative aspects of the "war on terror" in Iraq. Again, credibility of a country's leadership is the key to conditioning the effects of high-level visits on the foreign public's perception of the country's policy. The most recent finding shows that high-level diplomatic visits across the board can improve the public approval of the visiting leader's job performance by a significantly large effect. The positive messages are especially contingent on how the public-diplomacy activities are mentioned in the news in the host countries [@goldsmith_does_2021].

@@

However, while public diplomacy is one way to increase a state's soft power, in the end, visits and media are fleeting and symbolic. To reinforce the objectives pursued through these visible acts of diplomacy, we argue that Beijing uses other tools, such as foreign aid, to provide material support to important countries. Hence, we expect that to the extent that Beijing uses foreign aid as a tool in support of these particular foreign policy goals, we should see Chinese development finance parallel these different but complementary activities. This rationale leads to our hypotheses:

@@

To assess complementarities between China's bilateral diplomatic visits and state sponsored media coverage of developing countries with Beijing's bilateral development finance, we combine data from multiple sources. We merge AidData's Chinese development finance dataset [@dreherEtAl2021 and @dreherEtAl2022] with two newly available datasets: (1) AidData's compiled yearly counts of bilateral official diplomatic visits from China [@aidData2021] and (2) millions of English edition *Xinhua* news articles from 2000 to 2014 scraped by the Cline Center for Advanced Social Research [-@cline2022]. The full dataset consists of unique recipient-year observations from 2000 to 2014.[^7]

[^7]: Version 1.0 of the Chinese development finance dataset may be obtained at: <http://aiddata.org/data/chinese-global-official-finance-dataset>. The data on China's public diplomacy can be obtained at: <http://china-dashboard.aiddata.org/>. Finally, the Archer portal used to access extracted features in the Global News Index at the Cline Center can be found at: <https://databank.illinois.edu/datasets/IDB-2179938>.

@@

The first set of controls consist of aid recipient characteristics. From the Penn World Table (version 9.1), we use real gross domestic product (GDP) in millions of 2011 USD [@feenstraEtAl2015].[^8] This serves as a proxy for the size of a recipient's economy. From the Penn World Table we also use population in millions and the number of people employed in millions. We normalize values using ihs to keep the transformation of the data consistent with that of the response. From the Institute for Health Metrics and Evaluation we use a yearly count of the number of individuals killed by natural disasters, and we again apply the ihs transformation [-@gbdcn2021].[^9] From PRIO/UCDP we use a binary measure of the presence of civil war, coded as 1 for each year where there is armed violence between two or more parties where one of the parties is the government and at least 25 battle-related deaths occur [@gleditschEtAl2002; @petterssonEtAl2021].[^10] To capture political and civil liberties we use Freedom House and adjust values so that higher values denote greater levels of freedom.[^11] We use this measure instead of Polity to avoid collinearities with civil war.

[^8]: Available at <https://doi.org/10.15141/S50T0R>.

[^9]: Available at <https://ghdx.healthdata.org/gbd-results-tool>.

[^10]: Available at <https://ucdp.uu.se/downloads/index.html#armedconflict>.

[^11]: Available at <https://freedomhouse.org/>.

We further control for bilateral characteristics between China and aid recipients. We account for bilateral distance in kilometers between China and developing countries using the distance measure from CEPII's gravity dataset [@mayerZignago2011]. To adjust for economic interests, we account for bilateral trade, data for which comes from CEPII's TRADEHIST dataset [@fouquinHugot2016].[^12] The former is log-transformed, while the latter is transformed via the inverse hyperbolic sine. Finally, to account for geostrategic interests, we use the alliance measure from the ATOP database, which takes the value 1 if Beijing and a recipient share an formal military alliance [@leedsEtAl2002].[^13]

[^12]: Both available at <http://www.cepii.fr/cepii/en/bdd_modele/bdd.asp>.

[^13]: Available at <http://www.atopdata.org/>.

@@

Results are shown for `r scales::comma(nrow(dt %>% filter(year!=2000)))` unique recipient-year observations from 2001 to 2014. Multiple imputation for missing values in covariates was done via chaining random forests combined with predictive mean matching, which ensures imputed values do not differ from values already present in the data (such as in the case of a binary variable) and that the conditional distributions have realistic variances.[^14] Summary statistics are shown the Appendix.

[^14]: For multiple imputation we used the `missRanger` R package. See @stekhovenBuhlmann2011 for more on the method and its robustness relative to other approaches.

@@

```{r eval=FALSE, include=FALSE}
coef_table <- map_dfr(
  model_list,
  ~ estimatr::tidy(lmtest::coeftest(.x))
) %>%
  filter(
    str_detect(term, "count") | 
      str_detect(term, "visits")
  ) %>%
  mutate(
    conf.low = estimate - 1.96 * std.error,
    conf.high = estimate + 1.96 * std.error,
    term = rep(c("Coverage", "Visits"), len = n())
  ) %>%
  select(term, estimate, conf.low, conf.high)
tibble(
  "1" = coef_table$term[1:2],
  "2" = coef_table$estimate[1:2],
  "3" = " ",
  "4" = coef_table$estimate[3:4],
  "5" = " ",
  "6" = coef_table$estimate[5:6],
  "7" = " ",
  "8" = coef_table$estimate[7:8],
  "9" = " ",
  "10" = coef_table$estimate[9:10],
  "11" = " ",
  "12" = coef_table$estimate[11:12],
  "13" = " "
) %>% 
  mutate_if(is.numeric, function(x) round(x, 2)) %>%
  kable(booktabs = T,
        format = "latex",
        caption = "Table 1: Model Estimates",
        col.names = c(
          " ", rep(c("Est.", "95% CI"), len = 12)
        )) %>%
  kable_classic(full_width = F) %>%
  column_spec(
    3, image = spec_pointrange(
      x = coef_table$estimate[1:2],
      xmin = coef_table$conf.low[1:2],
      xmax = coef_table$conf.high[1:2],
      vline = 0
    )
  ) %>%
  column_spec(
    5, image = spec_pointrange(
      x = coef_table$estimate[3:4],
      xmin = coef_table$conf.low[3:4],
      xmax = coef_table$conf.high[3:4],
      vline = 0
    )
  ) %>%
  column_spec(
    7, image = spec_pointrange(
      x = coef_table$estimate[5:6],
      xmin = coef_table$conf.low[5:6],
      xmax = coef_table$conf.high[5:6],
      vline = 0,
      lim = c(0, max(coef_table$conf.high[5:6]))
    )
  ) %>%
  column_spec(
    9, image = spec_pointrange(
      x = coef_table$estimate[7:8],
      xmin = coef_table$conf.low[7:8],
      xmax = coef_table$conf.high[7:8],
      vline = 0
    )
  )%>%
  column_spec(
    11, image = spec_pointrange(
      x = coef_table$estimate[9:10],
      xmin = coef_table$conf.low[9:10],
      xmax = coef_table$conf.high[9:10],
      vline = 0
    )
  ) %>%
  column_spec(
    13, image = spec_pointrange(
      x = coef_table$estimate[11:12],
      xmin = coef_table$conf.low[11:12],
      xmax = coef_table$conf.high[11:12],
      vline = 0
    )
  ) %>%
  add_header_above(
    c(
      " " = 1,
      "Linear" = 2,
      "Tobit" = 2,
      "Selection" = 2,
      "Level" = 2,
      "IV Lag" = 2,
      "IV Lewbel" = 2
    )
  )
